STAT 253 Final Project

### 2022-10-12 Final_Project_Work_HW2.Rmd
Work

@@

spline_rec <- full_rec %>%
     step_ns(Runtime, deg_free = edf) %>% 
     step_ns(IMDB_Rating, deg_free = edf) %>%
     step_ns(No_of_Votes, deg_free = edf)

@@

fit_resamples(
    movie_wf,
    resamples = data_cv8, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()
```

>>>>

```{r}
gam_spec <- 
  gen_additive_mod() %>%
  set_engine(engine = 'mgcv') %>%
  set_mode('regression')

gam_mod <- fit(gam_spec,
    Gross ~ s(Runtime) + IMDB_Rating + s(Meta_score) + s(No_of_Votes) + Genre_1,
    data = imdb_clean 
)

```

```{r}
gam_mod %>% pluck('fit') %>% mgcv::gam.check() 
```

```{r}
gam_mod %>% pluck('fit') %>% plot()
```

@@

spline_rec <- full_rec %>%
     step_ns(Runtime, deg_free = 2) %>% 
    step_ns(Meta_score, deg_free = 2) %>%
     step_ns(No_of_Votes, deg_free = 6)

@@

fit_resamples(
    movie_wf,
    resamples = data_cv10, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()
```
